---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

#  Get Walk Scores from the Walk Score API

<!-- badges: start -->

[![R-CMD-check](https://github.com/chris31415926535/walkscore/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/chris31415926535/walkscore/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

 This package provides a tidy interface to the Walk Score API, a proprietary
 API that measures a location's "walkability" using a number between 0 and 100.

 The Walk Score API has a free tier which allows 5,000 API calls per day, and
 paid tiers with higher limits.

 This function makes it easy to spread your API calls out over a few days. When
 you call the function for the first time, if necessary it creates a new column
 of walks cores and assigns each row `NA`. Then, each row's walk score is populated
 as the function gets a good API response. The function breaks automatically
 upon detecting a rate limit, returning all results collected so far. When your
 rate limit resets and you call the function again, it picks up from the first
 `NA` walk score it finds and continues on. So make sure to save your results
 after each batch, but you don't need to keep track of fine-grained batch issues
 or worry about losing a whole batch if a response errors out--the function
 handles that for you.

 You'll need a valid Walk Score API key to use this package.

 **Please Note** neither this package nor its author are affiliated with Walk
 Score in any way, nor are any warranties made about this package or any data
 available through the Walk Score API. "Walk Score" is copyrighted and a
 registered trademark of its owner, *again, with whom we are not affiliated*.

 API documentation is available here: [https://www.walkscore.com/professional/api.php](https://www.walkscore.com/professional/api.php)


## Installation

You can install the development version of walkscore like so:

``` r
devtools::install_github("https://github.com/chris31415926535/walkscore")
```

## Example

```{r eval=FALSE}

library(dplyr)
library(walkscore)

your_apikey <- "put a real API key here"

test_data <- dplyr::tibble(lat = 45.420193, lon = -75.697796) |>
  walkscore::walkscore(apikey = your_apikey)


```


